MP MetaAnalysis

### 2018-10-15 Paper_Analyses.Rmd

---
title: "MP MetaAnalysis"
author: "Christina Bergmann and Katie Von Holzen"
date: '`r format(Sys.Date(), "%d %B, %Y")`'
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)

@@

r2 <- function(x){ round(x, 2)}

psig <- function(x){
  ifelse(x < .0001, "< .0001",
         ifelse(x < .001, "< .001",
                ifelse(x < .01, "< .01",
                       ifelse(x > .01 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))))
}

@@

cur_dir <- getwd()

@@

#Preparation

Read in data and tidy up dataset

```{r ReadIn,  echo = FALSE}

@@

```{r Preprocess, echo = FALSE}

@@

Plotting defaults

```{r PlotAPATheme, echo = FALSE}
#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014). In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009). Figure X plots our PRISMA flowchart.

@@

```{r SummaryTable, echo = FALSE}

@@

kable(Sum_table)

@@

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!

@@

```{r DescriptivesPubtype, echo = FALSE}

@@

kable(pub_info)

pi <- dat[,c("short_cite", "publication_status")]
pi <- unique(pi)

c.plot <- ggplot(pi, aes(x= publication_status)) + 
  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
  geom_bar(stat="count")+
  coord_cartesian(ylim = c(0, 30))+
  apatheme+
  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
        axis.title.x = element_blank())

c.plot

  jpeg(filename = "figures/Pub_count.jpg", 
       width = 500, height = 500, units = "px")

  c.plot

@@

The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., in press). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics: 
1 Condition: Were words mispronounced or not;
2 Mean age reported per group of infants, in days;
3 Vocabulary size:  
4 Size of mispronunciation, measured in features changed;
5 Distractor familiarity: familiar, unfamiliar;
6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
7 Position of mispronunciation: onset, medial, offset;
8 Type of mispronunciation: consonant, vowel;

We separated out conditions according to whether or not the target word was mispronounced to be able to investigate both infants' looking to the target picture separated by whether or not words were mispronounced and their mispronunciation sensitivity, which is the difference between looking in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).  The fact that the same infants have contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(dat)` records in our data.

@@

kable(comparison_info)
#table(db_ET_MP$es_method)
```
```{r DescriptivesES, echo = FALSE}
#how did we calculate effect sizes?

@@

All scripts and raw data are available on Open Science Framework (OSF). INSERT LINK AS FOOTNOTE HERE. Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper. Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for the pre-naming phase from the PTL score for the post-naming phase. When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced). Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with chance (50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`)). For these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.

We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (mispronunciation sensitivity). The effect size we report in the present paper are based on comparison of means, standardized by their variance. The most well-known effect size from this group is Cohen's *d* (Cite cohen). To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).

No authors made their raw data available. Instead, we calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. One paper reported this correlation, while we were able to compute correlations using means, standard deviations, and t-values (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, submitted). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We computed a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R (R citation) package metafor (Viechtbauer, 20XX, Multulevel reference). This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.

@@

In the psychological sciences, there is a documented reluctance to publish null results. As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012). To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests. We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R (R Core Team, 2016) package metafor (Viechtbauer, 2010). Effect szes with low-variance are closer to the estimated mean, while effect sizes with high-variance show an increased, evenly-distributed spread around the estimated mean. Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; Simonsohn, Simmons, & Nelson, 2014). This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices. Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.

@@

The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R (R Core Team, 2016) package metafor
(Viechtbauer, 2010). To investigate how development impacts mispronunciation sensitivity, our core theoretical investigation, we introduce age (centered; in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model. For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).

@@

```{r FunnelPlotAsymm_correct, echo = FALSE}

@@

```{r FunnelPlotAsymm_misp, echo=FALSE}

@@

Figure 1 plots the funnel plots for object identification for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016). Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`). These results, in conjunction with the assymmetric funnel plot (Figure 1) indicate bias in the literature. This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e. smaller variance) than expected (top left, outside the triangle).

```{r FunnelPrep, echo = FALSE}
### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

@@

```{r FunnelCorrect, echo = FALSE}

#Rename a bunch of things for ease
dat_co = db_ET_correct
#dat_co=db_ET_correct
dat_co <-
  dat_co %>% 
  rename(cite = short_cite,
         yi = g_calc,
         vi = g_var_calc)

@@

dat_co <-
  dat_co %>% 
  select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
  arrange(desc(yi))

@@

```{r FunnelMisp, echo = FALSE}

  #Rename a bunch of things for ease
dat_mp = db_ET_MP  
#dat_mp=db_ET_MP
  dat_mp <-
    dat_mp %>% 
    rename(cite = short_cite,
           yi = g_calc,
           vi = g_var_calc)

@@

  dat_mp <-
    dat_mp %>% 
    select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
    arrange(desc(yi))

@@

```{r FunnelCombo, echo = FALSE}

@@

```{r PcurveExport, echo = FALSE}

@@

```{r ReadIn_pcurve_app,  echo = FALSE}

curdir <- getwd()

@@

# this gives the number of significant results
# the Z value
# and the significance
pcd_correct <- pcurve_app("p_curve_co.txt",paste0(curdir, "/p_curve_app"))

pcd_misp <- pcurve_app("p_curve_mp.txt",paste0(curdir, "/p_curve_app"))

@@

We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions. The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, p `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05. The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, p `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.

Taken together, these results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies. Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

@@

We first calculated the meta-analytic effect for object identification in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges’ *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research) and that it is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size Hedges’ g was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated. But, as the p-curve indicated evidential value, we are confident in this result as well.

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, p `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, p `r psig(rma_MP$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we then compared the effect size Hedges’ *g* for correct pronunciations with mispronunciations, merging the two datasets. The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, p `r psig(rma_MPeffect$QMp)`.  Hedges’ *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the two type of responses were significantly different from one another (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.

@@

To evaluate the different predictions for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, p `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, p `r psig(rma_MP_age$QMp)`). The lack of a significant modulation indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

@@

@@

>>>>

---
title: "MP MetaAnalysis"
author: "Christina Bergmann and Katie Von Holzen"
date: '`r format(Sys.Date(), "%d %B, %Y")`'
output: 
  pdf_document:
    toc: true

bibliography: references.bib
---
```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

### Load libraries

library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)
library(poibin)
library(tidyverse)

@@

r2 <- function(x){ round(x, 3)}

#[CHRISTINA: I prefer exact p-values with more granularity]

psig <- function(x){
  ifelse(x < .001, "< .001",
         #ifelse(x < .001, "< .001",
                #ifelse(x < .01, "< .01",
                       ifelse(x > .001 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))#))
}

@@

# [CHRISTINA This should not be necessary]
#cur_dir <- getwd()

@@

```{r ReadIn}

@@

```{r Preprocess}

@@

```{r PlotAPATheme}
# Plotting defaults

#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014). The most recent version is available via the website and the interactive platform MetaLab (metalab.stanford.edu; Bergmann et al., 2018). Since the present paper was written with embedded analysis scripts in R [@R], it is always possible to re-analyze an updated dataset. In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009). Figure X plots our PRISMA flowchart.

@@

```{r SummaryTable}

@@

kable(Sum_table, col.names = c("Paper", "Age", "Vocabulary", "# Features", "Distractor", "Distractor name overlap", "MP Position", "MP Type"))

@@

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]

@@

```{r DescriptivesPubtype}

@@

kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))

# Not sure about this plot
#pi <- dat[,c("short_cite", "publication_status")]
#pi <- unique(pi)

#c.plot <- ggplot(pi, aes(x= publication_status)) + 
#  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
#  geom_bar(stat="count")+
#  coord_cartesian(ylim = c(0, 30))+
#  apatheme+
#  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
#        axis.title.x = element_blank())

#c.plot

#  jpeg(filename = "figures/Pub_count.jpg", 
#       width = 500, height = 500, units = "px")

#  c.plot

#  dev.off()

@@

The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics:   
1 Condition: Were words mispronounced or not;  
2 Mean age reported per group of infants, in days;  
3 Vocabulary size, measured by a standardized questionnaire or list;    
4 Size of mispronunciation, measured in features changed;  
5 Distractor familiarity: familiar or unfamiliar;  
6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
7 Position of mispronunciation: onset, medial, offset, or mixed;  
8 Type of mispronunciation: consonant, vowel, or both.

We separated out conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture separated by whether or not words were mispronounced as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(dat)` records in our data.

@@

kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
#table(db_ET_MP$es_method)
```

```{r DescriptivesES}
#how did we calculate effect sizes?

@@

#[KATIE] Can you also rename the factors here (like t_one)?
#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not. 
```

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper. Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase. When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced). Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`). For all these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more relative increase in looks to the target.

We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e. mispronunciation sensitivity). The effect size we report in the present paper are based on comparison of means, standardized by their variance. The most well-known effect size from this group is Cohen's *d* [@cohen]. To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. One paper reported this correlation [CHRISTINA: Can we cite this??]; we were able to compute correlations using means, standard deviations, and t-values [CHRISTINA: can we add N?] (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor]. This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.

@@

[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]

In the psychological sciences, there is a documented reluctance to publish null results. As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012). To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests. We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor]. Effect sizes with low-variance are expected to fall closer to the estimated mean, while effect sizes with high-variance should show an increased, evenly-distributed spread around the estimated mean. Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices. Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.

@@

The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R [@R] package metafor [@metafor]. To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduce age (centered; continuous and measured in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model. For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).

[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all. For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]

@@

```{r FunnelPlotAsymm_correct}

@@

```{r FunnelPlotAsymm_misp}

@@

Figure 1 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016). Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`). These results, quantifying the assymmetry in the funnel plots (Figure 1), indicate bias in the literature. This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e. smaller variance) than expected (top left, outside the triangle).

[CHRISTINA: If we want to interpret here, how about the next bit.]

The stronger publication bias for correct pronunciation might reflect the status of this condiction as a control. If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions. However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as population infants would reliably show the expected object identification effect.

We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias. The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.  [CHRISTINA: I have to add some bits here.]

```{r FunnelPrep}
### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

@@

```{r FunnelCorrect}

#Rename a bunch of things for ease
dat_co = db_ET_correct %>% 
  rename(cite = short_cite,
         yi = g_calc,
         vi = g_var_calc) %>%
  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
  dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>%
  arrange(desc(yi))

@@

@@

```{r FunnelMisp}

  #Rename a bunch of things for ease
dat_mp = db_ET_MP %>%
    rename(cite = short_cite,
           yi = g_calc,
           vi = g_var_calc) %>%
    dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
    arrange(desc(yi))

@@

@@

```{r FunnelCombo}

@@

```{r PcurveExport}

@@

```{r ReadIn_pcurve_app,  echo = FALSE, error = FALSE}

@@

# this gives the number of significant results
# the Z value
# and the significance
pcd_correct <- pcurve_app("p_curve_co.txt", "p_curve_app")
```

```{r ReadIn_pcurve_app_2,  echo = FALSE, error = FALSE}
pcd_misp <- pcurve_app("p_curve_mp.txt", "p_curve_app")

@@

We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions. The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05. The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.

[CHRISTINA: CAn you add the stats for the non-sig results?]

Taken together, these results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

@@

We first calculated the meta-analytic effect for object identification, i.e. looks to the target image in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.

[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated. But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error. We therefore continue with our moderator analysis.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets. The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, *p* `r psig(rma_MPeffect$QMp)`.  Hedges' *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the responses across conditions were significantly different (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`). This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, *p* `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, *p* `r psig(rma_MP_age$QMp)`). The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value

@@

[cHRISTINA] I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH HERE OR FLIP THE PARAGRAPH AROUND:
1. ARE DIFFERENT MODERATORS USED AT DIFFERENT AGES? 
TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
2. WHICH MODERATORS INFLUENCE MP SENSITIVITY
TEST SIMPLE MA WITH MODERATOR TESTS

OR 
"FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS INFANTS MATURE, I.E. WHETHER OLDER INFANTS ARE TESTED ON A MORE DIFFICULT TASK "
ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES, AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY

@@

# References
